---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rOpenEpi: R Port of Open Source Epidemiologic Statistics for Public Health

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

This package is the R port for the free and open source software [OpenEpi](https://www.openepi.com). [OpenEpi](https://www.openepi.com) provides statistics for counts and measurements in descriptive and analytic studies, stratified analysis with exact confidence limits, matched pair and person-time analysis, sample size and power calculations, random numbers, sensitivity, specificity and other evaluation statistics, R x C tables and chi-square for dose-response. The original software was written in JavaScript and HTML and was designed to be a serverless, browser-based application that can be used on any computer platform including smartphones. With the advent of Shiny in R, re-creating the [OpenEpi](https://www.openepi.com) browser-based application has become possible. This package translates the JavaScript calculator functions used in the original application into R and includes a Shiny application that uses these functions to replicate the original [OpenEpi](https://www.openepi.com) browser application.

## Installation

`rOpenEpi` is not yet available via [CRAN](https://CRAN.R-project.org).

You can install the development version of rOpenEpi from [GitHub](https://github.com/ernestguevarra/rOpenEpi) with:

```{r install, echo = TRUE, eval = FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("ernestguevarra/rOpenEpi")
````

<!---
You can install the released version of rOpenEpi from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rOpenEpi")
```
--->


